---
title:    'AdvRPackage'
author:   "Author: Daniel Carpenter"
date:     "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  github_document:
    toc: yes
    toc_depth: 4
  # html_document:
  #   toc: yes
  #   toc_float: yes
  #   toc_depth: 3
  #   theme: yeti
  #   fig_width: 7
  #   fig_height: 5
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  echo    = TRUE, # Default only show output (not code)
  message = FALSE,
  warning = FALSE
)
```

# `AdvRPackage`

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of `AdvRPackage` from [GitHub](https://github.com/Daniel-Carpenter/AdvRPackage.git) with:

``` r
# install.packages("devtools")
devtools::install_github("Daniel-Carpenter/AdvRPackage")
```


## Installment 4 Requirements

### Load Package
```{r loadPackage_I4}
library(AdvRPackage) # My package: https://github.com/Daniel-Carpenter/AdvRPackage
```

### Printed Functions
```{r funs} 
# Print function
print(AdvRPackage::myttest)

# Print function
print(AdvRPackage::print)

# Plot function
print(AdvRPackage::plot)
```


<br>

### Run the code for Installment 4
```{r code_I4}
# Create sample data
set.seed(21); x <- rnorm(30, 5, 2); 
set.seed(23); y <- rnorm(30, 3, 2); alpha <- 0.05

# Run the t-test function using this package
obj <- AdvRPackage::myttest(x = x, y = y, alpha = 0.05)

# Print Method 
print(obj)
```

```{r}
plot(obj)
```


<br>

## Examples (For Final Package)
> Note that this section may not be required for Installment 4, but is required for the final installment

### Load Package
```{r loadPackage}
library(AdvRPackage) # My package: https://github.com/Daniel-Carpenter/AdvRPackage
```

<br>

---

### Test `1` - Default T-Test

* Notice the *non*-disparate distributions. The program will detect *equal* variances
and use a `Default` T-Test.

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 15)
set.seed(35); y = rnorm(30, mean = 8, sd = 15)

# Run the t-test function using this package
ans1 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = FALSE)

# Print Method 
print(ans1)
```

```{r}
# Plot Method 
plot(ans1)
```


<br>

---

### Test `2` - Welch T-Test

* Notice the *disparate* distributions. The program will detect *non*-equal variances
and use a `Welch` T-Test.

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 5)
set.seed(35); y = rnorm(30, mean = 8, sd = 15)

# Run the t-test function using this package
ans2 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = FALSE)

# Print Method 
print(ans2)
```

```{r}
# Plot Method 
plot(ans2)
```


<br>

---

### Test `3` - Paired T-Test

* Notice that when a `Paired` T-Test is detected, it will plot the distribution 
of sample differences

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 15)
set.seed(35); y = x + rnorm(30, 5 , 4)

# Run the t-test function using this package
ans3 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = TRUE)

# Print Method
print(ans3)
```

```{r}
# Plot Method 
plot(ans3)
```


