---
title:    'Introduction to AdvRPackage'
author:   "Daniel Carpenter"
date:     "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
    fig_width: 7
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{Introduction to AdvRPackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/README-",
  out.width = "100%",
  echo    = TRUE, # Default only show output (not code)
  message = FALSE,
  warning = FALSE
)
```

> In the vignette, we demonstrate the usage of the `AdvRPackage` developed by Daniel Carpenter. This package provides an advanced T-Test function for R users. The package can be installed from GitHub using the `devtools` package.

# Installation

You can install the development version of `AdvRPackage` from [GitHub](https://github.com/Daniel-Carpenter/AdvRPackage.git) with:

``` r
# install.packages("devtools")
devtools::install_github("Daniel-Carpenter/AdvRPackage")
```


<br>

# Usage

In the following examples, we demonstrate how to use the `myttest` function for different scenarios.

## Load Package

First, load the `AdvRPackage` package:

```{r loadPackage}
library(AdvRPackage) # Seen at: https://github.com/Daniel-Carpenter/AdvRPackage
```

Now, let's use the `myttest()` function to perform various types of T-Tests. 

## *Default* T-Test

For two groups with *equal* variances, the function will perform a *default* T-Test. Users can create sample data, run the T-Test function using the package, and `print` the results. The corresponding plot can also be displayed with the `plot` function.

First, create some random data that has *similar* variances.

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 15)
set.seed(35); y = rnorm(30, mean = 8, sd = 15)

# Run the T-Test function using this package and creating a Rttest object
ans1 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = FALSE)
```

To print the `Rttest` object, use the `print()` function. You will find helpful summary statistics and parameters in HTML output:

```{r}
# Print Method 
print(ans1)
```

To plot the `Rttest` object, use the `plot()` function:

In the plot, you can notice the *non*-disparate distributions. The program will detect *equal* variances and use a *Default* T-Test.

```{r}
# Plot Method 
plot(ans1)
```


<br>

## *Welch* T-Test

For two groups with *unequal* variances, the function will perform a *Welch* T-Test. The process is similar to the *Default* T-Test, with the only difference being the data generated to have *unequal* variances.

First, create some random data that has *unequal* variances.

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 5)
set.seed(35); y = rnorm(30, mean = 8, sd = 15)

# Run the T-Test function using this package and creating a Rttest object
ans2 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = FALSE)
```

To print the `Rttest` object, use the `print()` function as seen before. You will find helpful summary statistics and parameters in HTML output:

```{r}
# Print Method 
print(ans2)
```

To plot the `Rttest` object, use the `plot()` function as seen before:

In the plot, you can notice the *disparate* distributions. The program will detect *non*-equal variances and use a *Welch* T-Test.

```{r}
# Plot Method 
plot(ans2)
```


<br>

## *Paired* T-Test

For *paired* data, the function will perform a *paired* T-Test. To run the *paired* T-Test, users need to set the `paired` parameter to `TRUE.` Using the `plot()` function, you can plot the distribution of sample differences too.

First, create some random data:

```{r}
# Create sample data
set.seed(32); x = rnorm(30, mean = 10, sd = 15)
set.seed(35); y = x + rnorm(30, 5 , 4)

# Run the T-Test function using this package and creating a Rttest object
ans3 = AdvRPackage::myttest(x, y, alpha = 0.05, paired = TRUE)
```

To print the `Rttest` object, use the `print()` function as seen before. You will find helpful summary statistics and parameters in HTML output:

```{r}
# Print Method
print(ans3)
```

To plot the `Rttest` object, use the `plot()` function as seen before:

In the plot, you can notice that when a *Paired* T-Test is detected, it will plot the distribution of sample differences and the associated confidence interval based on the `alpha` parameters in the `Rttest` object.

```{r}
# Plot Method 
plot(ans3)
```
